---
title: "Swarna Data Exploration"
author: "Vishnu Sharma & Abhishek Kanaparthi"
date: "November 5, 2017"
output: html_document
---

The following Document elucidates the various analytics carried out on the Swarna River Data.
The Dataset is preloaded into the environment under the name swarnaData.

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(readxl)
swarnaData <- read_excel("R:/Vishnu Sharma Projects/Swarna River Project/SwarnaData.xlsx")
```

```{r, message=FALSE, warning=FALSE}
attach(swarnaData) # Loading the Data into the environment
str(swarnaData) # Checking the structure of the Data
summary(swarnaData) # Checking the Summary of the data features
```

We can observe above that the variables Transect_Location, Stream, Season are converted as character, we need to convert them into factors and check the structure of data again.

```{r}
swarnaData$Transects_Location= factor(swarnaData$Transects_Location)
swarnaData$Stream = factor(swarnaData$Stream)
swarnaData$Season = factor(swarnaData$Season)
```

After converting the above as factors, now lets go ahead and check the structure of the data and summary again.

```{r}
str(swarnaData) # Rechecking the Structure of the data
summary(swarnaData) # rechecking the Summary of the data
```

The next step is to check the corelations between the variables and their distributions.

```{r, message=FALSE, warning=FALSE}
library(psych)
NumberCols = c(3:8,10) # Columns with Important Data, Numerical ones only
pairs.panels(swarnaData[NumberCols])
```

